Supplemental Materials for the paper: \\ Pesticide exposure in small streams in Germany

### 2016-10-19 supplement/Supplemental_Materials.tex
more fixes, typos etc

\documentclass[pdftex,a4paper]{scrreprt}
\usepackage[utf8]{inputenc}       
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{booktabs} % table rulers
\usepackage{longtable} % multipage tables
\usepackage{todonotes}
\usepackage{amsmath}
\usepackage{float} % for [H]

@@

\begin{enumerate}
	\item Structure: Structure has been adjusted to the database structure.
	\item Coordinates: Coordinates have been transformed to a common Coordinate Reference System (DHDN / 3-Grad Gauss-Krüger Zone 3 (EPSG:31467)) and duplicates merged.
	\item Chemicals: Chemical names and identifiers have been unified using the webchem package \citep{szocs_webchem:_2016}.
	\item  Identifiers: Unique identifiers have been assigned.
	\item Units: All concentrations have been converted to $\mu g/L$. Values below limit of quantification have be set to zero.
	\item Other meta-data: meta-data has been standardised.
	\item Temporal resolution: The temporal resolution of the database is 1 day. Date below this resolution has been aggregated by maximum.
	\item Validity Checks: Simple rules for validity checks have been implemented (e.g. no negative concentrations).
\end{enumerate}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width = 0.8\textwidth]{prac_ex}
	\caption[Cumulative distribution of the number sites exceeding RAC.]{Cumulative distribution of sites exceeding RAC. Dotted lines indicate fraction of sites exceeding a RQ of 1 and 0.1. 23\% of sites showed no detection of compounds with RAC and are not shown due to logarithmic x-axis.}
	\label{fig:pdetects}
\end{figure}

@@

\bibliographystyle{apalike}      % basic style, author-year citations
\bibliography{references}

>>>>

\documentclass[pdftex,a4paper]{scrreprt}
\usepackage[utf8]{inputenc}       
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{booktabs} % table rulers
\usepackage{longtable} % multipage tables
\usepackage{todonotes}
\usepackage{amsmath}
\usepackage{float} % for [H]
\usepackage{array, ragged2e}
\newcolumntype{R}[1]{>{\RaggedLeft\arraybackslash}p{#1}} % right aling column with fixed width

@@

\begin{enumerate}
	\item Structure: Structure has been adjusted to the database structure.
	\item Coordinates: Coordinates have been transformed to a common Coordinate Reference System (DHDN / 3-Grad Gauss-Krüger Zone 3 (EPSG:31467)) and duplicates merged.
	\item Chemicals: Chemical names and identifiers have been unified using the webchem package (\url{https://github.com/ropensci/webchem}).
	\item  Identifiers: Unique identifiers have been assigned.
	\item Units: All concentrations have been converted to $\mu g/L$. Values below limit of quantification have be set to zero.
	\item Other meta-data: meta-data has been standardised.
	\item Temporal resolution: The temporal resolution of the database is 1 day. Date below this resolution has been aggregated by maximum.
	\item Validity Checks: Simple rules for validity checks have been implemented (e.g. no negative concentrations).
\end{enumerate}

@@

\input{racdat}

\begin{figure}[ht]
	\centering
	\includegraphics[width = 0.8\textwidth]{prac_ex}
	\caption[Cumulative distribution of the number sites exceeding RAC.]{Cumulative distribution of sites exceeding RAC. Dotted lines indicate fraction of sites exceeding a RQ of 1 and 0.1. 23\% of sites showed no detection of compounds with RAC and are not shown due to logarithmic x-axis.}
	\label{fig:prac_ex}
\end{figure}

@@

% \bibliographystyle{apalike}      % basic style, author-year citations
% \bibliography{references}
